---
title: "Indiana Mesocosm Experiment"
author: "Laura Lopez & Meghan Duffy"
date: "23/04/2021 & Jan-June 2022"
output:
  word_document: default
  pdf_document: default
---

# Initial stuff, including loading packages and importing data

##loading packages
```{r,message=F,warning=F}
library(Hmisc)
library(tidyverse)
library(RColorBrewer)
library(lsmeans)
library(ggsignif)
library(here)
# library(cowplot)
library(multcomp)
library(multcompView)
library(lme4)
library(nlme)
library(patchwork)
# library(ggpubr)
```

## loading files

```{r,message=F,warning=F}
# Tell R where files are stored
here::i_am("scripts/IndianaMesocosmExpt.Rmd")

# Load the data
indianadata<-readr::read_csv(here("data/indianadatano22.csv"))
indianadata$chaoborusfactor<-as.factor(indianadata$chaoborus)
summary(indianadata)

#Fix issue with weeks, so that they line up with this timeline:
#week 0 = Daphnia added
#week 1 = spores added
#weeks 2-9 = sampling
indianadata$time <- indianadata$time + 1

indianadata <- indianadata %>% mutate(metsch=recode(metsch,'No Parasites'='No parasites'))

#Subset data
indianadatametsch <- indianadata %>%
  filter(metsch == "Parasites")

indianadatanometsch <- indianadata %>%
  filter(metsch == "No parasites")

```

# Plots and analysis related to figure 1: infection prevalence and infected host density

## Infections

### Plot
```{r, plotting infection prevalence}
propinfovertimeplot<-ggplot(indianadatametsch,aes(time,y=propinfected,group=chaoborusfactor,color=chaoborusfactor,shape=chaoborusfactor)) +
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_se",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=4) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Predation treatment", shape = "Predation treatment") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw()+theme(panel.grid = element_blank()) +
  theme(legend.position = c(0.35, 0.75)) +
  theme(legend.key.size = unit(0.05, 'cm'), legend.title = element_text(size=10), #change legend title font size
        legend.text = element_text(size=8)) +
  labs(x="Time (weeks)")+
  labs(y="Proportion infected (I/N)") + 
  theme(axis.text.x = element_blank(),
                                        axis.title.x = element_blank() ) +
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9")) 
propinfovertimeplot

# ggsave(here("figures", "propinfovertimeplot.jpg"), propinfovertimeplot, units = "in", width = 6, height = 4, dpi = 300)

#density of infected hosts
infdensityovertimeplot<-ggplot(indianadatametsch,aes(time,y=infectedlnone,group=chaoborusfactor,color=chaoborusfactor,shape=chaoborusfactor)) +
  stat_summary(fun="mean",geom="line",size=1, show.legend = FALSE) +
  stat_summary(fun.data = "mean_se",show.legend=FALSE) + 
  stat_summary(fun="mean",geom="point",size=4,aes(shape=chaoborusfactor),show.legend=FALSE) +
  scale_shape_manual(values=c(15,16,17,18)) +
#  labs(color="Predator density \n(per L)") + 
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) + 
  theme_bw()+theme(panel.grid = element_blank()) + 
  labs(x="Time (weeks)") +
  labs(y="Infected prey density \n(I; LN prey per L + 1)") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9")) +
  theme(axis.text.x = element_blank(),
                                        axis.title.x = element_blank() ) 
infdensityovertimeplot

#inftimeseriesplot <- plot_grid(propinfovertimeplot, infdensityovertimeplot, labels = "auto", ncol = 1, align = "v")
#inftimeseriesplot

# ggsave(here("figures", "inftimeseriesplot.jpg"), inftimeseriesplot, units = "in", width = 4, height = 5.5, dpi = 300)

```


### Summarizing infection prevalence data for reporting values in manuscript
```{r, summarizing infection prevalence data}
indianadatametsch$totalinfected <- indianadatametsch$adultsinfected + indianadatametsch$juvenilesinfected
indianadatametsch$totaluninfected <- indianadatametsch$adultsnotinfected + indianadatametsch$juvenilesnotinfected

# remove time 1 for analysis
indianadatametschanalysis <- indianadatametsch %>%
  filter(time > 1)

indiana_infected_summary <- indianadatametschanalysis %>%
  group_by(time, chaoborusfactor) %>%
  summarise(meanpropinf = mean(propinfected), minpropinf = min(propinfected), maxpropinf = max(propinfected),  meaninfdensity = mean(totalinfected), mininfdensity = min(totalinfected), maxinfdensity = max(totalinfected)) 

indiana_infected_summary


```


### Analysis
```{r, analysis of infection prevalence over time}
# Initial analysis of time series data -- massively overdispersed so abandoned this approach
prevmodel1<-glm(cbind(totalinfected, totaluninfected) ~ chaoborus + (1|time), family=binomial(logit), data=indianadatametschanalysis) 
anova(prevmodel1, test="Chisq")
summary(prevmodel1)

# Testing for overdispersion (using code from Ben Bolker via Michelle Fearon)
overdisp_fun <- function(model) {
  rdf <- df.residual(model)
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}

overdisp_fun(prevmodel1)
# super overdispersed, going to focus on averages instead

#looking at means to avoid overdispersion issue:
infprevsummary <- indianadatametschanalysis %>%
  group_by(chaoborusfactor, metsch, tank) %>%
  summarise(meanpropinf = mean(propinfected)) 


infprevsummaryanalysis <- aov(meanpropinf~chaoborusfactor,data=infprevsummary)
summary(infprevsummaryanalysis)  

overdisp_fun(infprevsummaryanalysis)
#not overdispersed!

lsmeans(infprevsummaryanalysis,pairwise~chaoborusfactor,adjust="tukey")

```

## Average infection prevalence

```{r, plotting mean infection prevalence}
meaninfprevplot <- ggplot(infprevsummaryanalysis,aes(x=chaoborusfactor,y=meanpropinf,color=chaoborusfactor)) +
  geom_boxplot(show.legend=FALSE) +
  geom_jitter(shape=17, position=position_jitter(width=0.2, height=0), alpha = 0.5, color = '#787878', size = 2) +
  labs(y="Average \nproportion infected (I/N)") +
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw() +
  geom_text(data=infprevsummaryanalysis,x=2.3, y=0.18,label ="Predation: p = 0.0008", color="black",size = 2.5) +
  ylim(0.0,0.2) +
  theme(axis.text.x = element_blank(),
                                        axis.title.x = element_blank() ) +
  theme(panel.grid=element_blank())

meaninfprevplot

```


## Average LN infected host density

```{r, average infected host density analysis and plotting}
# weeks 2 through 9
infdenssummary <- indianadatametschanalysis %>%
  group_by(chaoborusfactor, tank) %>%
  summarise(meaninfdens = mean(infectedlnone)) 
  
infdenssummaryanalysis <- aov(meaninfdens~chaoborusfactor,data=infdenssummary)
summary(infdenssummaryanalysis)  

overdisp_fun(infdenssummaryanalysis)
#not overdispersed

lsmeans(infdenssummaryanalysis,pairwise~chaoborusfactor,adjust="tukey")

meaninfhostplot <- ggplot(infdenssummaryanalysis,aes(x=chaoborusfactor,y=meaninfdens,color=chaoborusfactor)) +
  geom_boxplot(show.legend=FALSE) +
  geom_jitter(shape=17, position=position_jitter(width=0.2, height=0), alpha = 0.5, color = '#787878', size = 2) +
  labs(x="Predation treatment (predators per L)",y="Average infected prey density \n(I; LN prey per L + 1)") +
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw() +
  geom_text(data=infdenssummaryanalysis,x=1.8, y=0.18,label ="Predation: p < 0.0001", color="black",size = 2.5) +
  ylim(0.0,1.6) +   
  theme(axis.text.x = element_blank(),
                                        axis.title.x = element_blank() ) +
  theme(panel.grid=element_blank())

meaninfhostplot

```

# Analyses and plots related to population density

## Plotting time series of density

```{r, population size over time}
indianadata$metsch <- as.factor(indianadata$metsch)

popdensitytimeseriesmetsch <- ggplot(indianadatametsch, aes(x = time, y = (logone), color = chaoborusfactor, group = chaoborusfactor, shape = chaoborusfactor)) + 
  stat_summary(fun = "mean", geom="line", aes(group = chaoborusfactor)) + 
  stat_summary(fun.data="mean_se") +
    stat_summary(fun="mean",geom="point",size=4,aes(shape=chaoborusfactor),show.legend=FALSE) +
  labs(x="Time (week)",y="Prey density \n(N; LN prey per L + 1)") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9")) + 
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
    scale_shape_manual(values=c(15,16,17,18)) +
  theme_bw()+theme(panel.grid = element_blank()) +
  ylim(0,5.0) +
  theme(axis.text.x = element_blank(),
                                        axis.title.x = element_blank() ) + 
  theme(axis.title.y = element_blank() ) +
    theme(legend.position = 'none')  
#+ 
#  ggtitle('Parasites') +
#  theme(plot.title = element_text(size = 10)) 

popdensitytimeseriesmetsch

popdensitytimeseriesnometsch <- ggplot(indianadatanometsch, aes(x = time, y = (logone), color = chaoborusfactor, group = chaoborusfactor, shape = chaoborusfactor)) + 
  stat_summary(fun = "mean", geom="line", aes(group = chaoborusfactor)) + 
  stat_summary(fun.data="mean_se") +
    stat_summary(fun="mean",geom="point",size=4,aes(shape=chaoborusfactor),show.legend=FALSE) +
  labs(x="Time (week)",y="Prey density \n(N; LN prey per L + 1)") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9")) + 
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
    scale_shape_manual(values=c(15,16,17,18)) +
  theme_bw()+theme(panel.grid = element_blank()) +
    ylim(0,5.0) +
    theme(axis.title.y = element_blank() ) +
    theme(legend.position = 'none')

#+ 
#  ggtitle('No parasites') +
#  theme(plot.title = element_text(size = 10)) 

popdensitytimeseriesnometsch


# ggsave(here("figures", "figure2.jpg"), figure2, units = "in", width = 6, height = 4, dpi = 300)

```

## Average total host density analysis

```{r, average total host density analysis}
# remove time 1 for analysis
indianadataanalysis <- indianadata %>%
  filter(time > 1)

densitysummary <- indianadataanalysis %>%
  group_by(chaoborusfactor, metsch, tank) %>%
  summarise(meandens = mean(logone)) 
  
densitysummaryanalysis <- aov(meandens~chaoborusfactor*metsch,data=densitysummary)
summary(densitysummaryanalysis)  

overdisp_fun(densitysummaryanalysis)
#not overdispersed

lsmeans(densitysummaryanalysis,pairwise~chaoborusfactor*metsch,adjust="tukey")

```
## Average total host density plot

```{r, average prey density plot}
meandensityplot <- ggplot(densitysummaryanalysis,aes(x=chaoborusfactor,y=meandens, color=chaoborusfactor, fill = metsch)) +
  geom_boxplot(lwd=0.75) +
  geom_point(pch=17, position=position_jitterdodge(jitter.width = 0.2), alpha = 0.5, size = 2, color = 'black',show.legend=FALSE) +
  labs(x="Predation treatment (predators per L)",y="Average prey density \n(N; LN prey per L + 1)") +
  labs(color = "Predator density \n(per L)", fill = "Parasite treatment") +
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black"), guide="none") +
  scale_fill_manual(values=c('white','gray')) +
  theme_bw() +   
  geom_text(data=densitysummaryanalysis,x=2.7, y=0.5,label ="Predation: p < 0.0001\nParasitism: p = 0.12\nPred*Para: p = 0.49", color="black",size = 2.5) +
  ylim(0.0,4.6) + 
  theme(panel.grid=element_blank()) +
      theme(legend.position = c(0.2, 0.38)) +
  theme(legend.key.size = unit(0.5, 'cm'), legend.title = element_blank(),
        legend.text = element_text(size=7)) 

meandensityplot


```

## Looking at evolution of resistance
## Clones over time: importing data, calculating weighted averages
```{r, import data needed to look at clonal changes over time}
evoldata<-readr::read_csv(here("data/genotype.frequencies_MHC_converted.csv"))
evoldata
#excluding tank 22
evoldata2<-evoldata[!(evoldata$tank=="22"),]
evoldata2$pred<-as.factor(evoldata2$predation)
evoldata2$round<-evoldata2$week+1
evoldata2$roundfactor<-as.factor(evoldata2$round)
summary(evoldata2)
evoldata2$para <- factor(evoldata2$Parasites, levels = c("1", "0"),
                  labels = c("Parasites", "No parasites"))

evoldata2$para <- factor(evoldata2$para, c("No parasites", "Parasites"))

```

```{r, calculating weighted averages}
#Note: "inf" is infection rate, beta. It is the product of the per spore susceptibility and the susceptible feeding rate.
BD0542inf <- 0.000000079776
BD0846inf <- 9.81E-08
BD1964inf	<- 0
CB2468inf	<- 8.15E-08
DW2258inf	<- 1.69E-07
DW2975inf	<- 1.53E-07
ML3082inf	<- 4.98E-08
ML3284inf	<- 1.37E-07
IL1443inf	<- 1.80E-07
  
BD0542inf_scaled <- 0.000000079776 * 10^7
BD0846inf_scaled <- 9.81E-08 * 10^7
BD1964inf_scaled	<- 0
CB2468inf_scaled	<- 8.15E-08 * 10^7
DW2258inf_scaled	<- 1.69E-07 * 10^7
DW2975inf_scaled	<- 1.53E-07 * 10^7
ML3082inf_scaled	<- 4.98E-08 * 10^7
ML3284inf_scaled	<- 1.37E-07 * 10^7
IL1443inf_scaled	<- 1.80E-07 * 10^7

evoldata2$infectionmean_scaled <- evoldata2$BD05.42*BD0542inf_scaled  +
  evoldata2$BD08.46*BD0846inf_scaled  +
  evoldata2$BD19.64*BD1964inf_scaled  +
  evoldata2$CB24.68*CB2468inf_scaled  +
  evoldata2$DW22.58*DW2258inf_scaled  +
  evoldata2$DW29.75*DW2975inf_scaled  +
  evoldata2$IL14.43*IL1443inf_scaled  +
  evoldata2$ML30.82*ML3082inf_scaled  +
  evoldata2$ML32.84*ML3284inf_scaled

# checking if things would be different if we used just per spore susceptibility (p)
BD0542p <- 5.54 * 10-4
BD0846p <- 5.64 * 10-4
BD1964p	<- 0
CB2468p	<- 5.25 * 10-4
DW2258p	<- 6.88 * 10-4
DW2975p	<- 5.77 * 10-4
ML3082p	<- 8.58 * 10-4
ML3284p	<- 4.93 * 10-4
IL1443p	<- 1.17 * 10-3

evoldata2$pmean <- evoldata2$BD05.42*BD0542p  +
  evoldata2$BD08.46*BD0846p  +
  evoldata2$BD19.64*BD1964p  +
  evoldata2$CB24.68*CB2468p  +
  evoldata2$DW22.58*DW2258p  +
  evoldata2$DW29.75*DW2975p  +
  evoldata2$IL14.43*IL1443p  +
  evoldata2$ML30.82*ML3082p  +
  evoldata2$ML32.84*ML3284p

#answer: no significant evolution of p
  
BD0542pred  <- 0.0197
BD0846pred  <- 0.0134
BD1964pred	<- 0.0116
CB2468pred	<- 0.0062
DW2258pred	<- 0.0144
DW2975pred	<- 0.0082
ML3082pred	<- 0.0157
ML3284pred	<- 0.0096
IL1443pred	<- 0.016

evoldata2$predationmean <- evoldata2$BD05.42*BD0542pred  +
  evoldata2$BD08.46*BD0846pred  +
  evoldata2$BD19.64*BD1964pred  +
  evoldata2$CB24.68*CB2468pred  +
  evoldata2$DW22.58*DW2258pred  +
  evoldata2$DW29.75*DW2975pred  +
  evoldata2$IL14.43*IL1443pred  +
  evoldata2$ML30.82*ML3082pred  +
  evoldata2$ML32.84*ML3284pred
```

```{r, sample sizes for genotyping}
evoldata2samplesizes <- evoldata2 %>%
  filter (week > 0) %>%
    group_by(tank, week) %>%
  summarise(meanhosts = mean(no.hosts.sampled)) 

# Used this to write the above results to a csv file, then added missing rows to that (with 0 as sample size)
# readr::write_csv(evoldata2samplesizes, here("data/evoldata2samplesizes.csv"))

# Now re-importing the version with zeroes. Not elegant, but gets the job done.
evoldata2samplesizeswithzeroes<-readr::read_csv(here("data/evoldata2samplesizeswithzeroes.csv"))

evoldata2samplesizeswithzeroessummary <- evoldata2samplesizeswithzeroes %>%
    group_by(pred, para, week) %>%
  summarise(meanhosts = mean(meanhosts)) 

evoldata2samplesizeswithzeroessummary2 <- evoldata2samplesizeswithzeroes %>%
    group_by(pred, para) %>%
  summarise(meanhosts = mean(meanhosts)) 

#readr::write_csv(evoldata2samplesizeswithzeroessummary, here("data/evoldata2samplesizeswithzeroessummary.csv"))

genotypingsamplesizes <- evoldata2samplesizeswithzeroes %>%
  summarise(meanhosts = mean(meanhosts)) 
```

## Evolution of infection resistance
```{r, plotting evolution of infection resistance}
evoldata2metsch <- evoldata2 %>%
  filter(para == "Parasites")

evoldata2nometsch <- evoldata2 %>%
  filter(para == "No parasites")

metschresevolplotmetsch <- ggplot(evoldata2metsch,aes(round,y=infectionmean_scaled,group=pred,color=pred,shape=pred)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_se",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=4,aes(shape=pred)) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred.", shape = "Pred.") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  ylim(0.5, 1.6) +
  labs(x="Time (weeks)") +
#  labs(y=expression(paste("Ave. infection rate, "*beta*", ("*"*10"^"-7"*")"))) + 
  scale_x_continuous(breaks=c(0,2,6,9)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
    theme(axis.text.x = element_blank(),
                                        axis.title.x = element_blank() ) +
    theme(axis.title.y = element_blank() ) +
  theme(legend.position = "none") 
#+
#  ggtitle('Parasites') +
#  theme(plot.title = element_text(size = 10)) 
metschresevolplotmetsch

metschresevolplotnometsch <- ggplot(evoldata2nometsch,aes(round,y=infectionmean_scaled,group=pred,color=pred,shape=pred)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_se",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=4,aes(shape=pred)) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred.", shape = "Pred.") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  ylim(0.5, 1.6) +
  labs(x="Time (weeks)") +
#  labs(y=expression(paste("Ave. infection rate, "*beta*", (L/hr/spore; "*"*10"^"-7"*")"))) + 
  scale_x_continuous(breaks=c(0,2,6,9)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
      theme(axis.title.y = element_blank() ) +
  theme(legend.position = "none") 
#+
#  ggtitle('No parasites') +
#  theme(plot.title = element_text(size = 10)) 
metschresevolplotnometsch

# ggsave(here("figures", "metschresevolplot.jpg"), metschresevolplot, units = "in", width = 6, height = 3.5, dpi = 300)

## checking for consistency of pattern with just p:
pevolplot <- ggplot(evoldata2,aes(round,y=pmean,group=pred,color=pred,shape=pred)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_se",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=4,aes(shape=pred)) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred.", shape = "Pred.") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  labs(x="Time (weeks)") +
  labs(y="Per spore susceptibility") + 
  scale_x_continuous(breaks=c(0,2,6,9)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
  facet_grid(rows=vars(para)) +
  theme(legend.position = "none") 

pevolplot
```

## Analysis related to Metsch susceptibility evolution
```{r, analysis of Metsch susceptibility evolution}
# removing week 0 for analysis
evoldata3 <- evoldata2 %>%
  filter(round != "0")

#infection susceptibility trait evolution analysis
infsuscmod1<-lme(infectionmean_scaled~pred+para+round+pred*para+pred*round+para*round+pred*para*round,random=~1|tank,data=evoldata3)
summary(infsuscmod1)
anova(infsuscmod1)
lsmeans(infsuscmod1,pairwise~round,adjust="tukey")
lsmeans(infsuscmod1,pairwise~para,adjust="tukey")


pmod1<-lme(pmean~pred+para+round+pred*para+pred*round+para*round+pred*para*round,random=~1|tank,data=evoldata3)
summary(pmod1)
anova(pmod1)
lsmeans(pmod1,pairwise~round,adjust="tukey")
lsmeans(pmod1,pairwise~para,adjust="tukey")

```

## Plotting evolution of infection resistance grouping predation treatments
```{r, plotting evolution of infection resistance grouping predation treatments}
metschresevolplotgrouped <- ggplot(evoldata2,aes(round,y=infectionmean_scaled,group=para,color=para,shape=para)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_se",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=3,shape=21,aes(fill=para)) +
  labs(color="Parasitism", fill="Parasitism") +
  scale_colour_manual(values=c("black","black")) +
  scale_fill_manual(values=c("white", "#857A8C")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  labs(x="Time (weeks)") +
  labs(y=expression(paste("Ave. infection rate, "*beta*", ("*"*10"^"-7"*")"))) + 
  scale_x_continuous(breaks=c(0,2,6,9)) +  
  ylim(0.5, 1.6) +
    geom_text(data=evoldata2,x=2.3, y=0.66,label ="Parasitism: p = 0.0334", color="black",size = 2.5) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
  theme(legend.position = c(2.5, 0.7)) +
        theme(axis.title.y = element_blank() ) +
  theme(legend.key.size = unit(0.05, 'cm'), legend.title = element_blank(),
        legend.text = element_text(size=8)) 

metschresevolplotgrouped

```



## Making one combined plot for figure 1
```{r, plot combining infection prevalence and infected density}
figure1 <- propinfovertimeplot + meaninfprevplot + infdensityovertimeplot + meaninfhostplot + (popdensitytimeseriesmetsch / popdensitytimeseriesnometsch) + meandensityplot + (metschresevolplotmetsch / metschresevolplotnometsch) + metschresevolplotgrouped +
  plot_layout(ncol = 2) + 
  plot_annotation(tag_levels = list(c('a', 'b', 'c', 'd', 'e', ' ', 'f', 'g', ' ', 'h'))) 

figure1

ggsave(here("figures", "figure1.jpg"), figure1, units = "in", width = 7, height = 11, dpi = 300)

# Note: I added a few of the labels in photoshop because I couldn't get it to look nice in R
```

# Analyses and figures related to Figure 3: chlorophyll and egg ratio
## Chlorophyll plot

```{r, chlorophyll data}
chlorodata<-readr::read_csv(here("data/indychlorono22.csv"))
chlorodata$chaoborus<-as.factor(chlorodata$chaoborus)
chlorodata$time<- chlorodata$time+1
chlorodata$time<-as.factor(chlorodata$time)
summary(chlorodata)

chlorodata$metsch <- factor(chlorodata$metsch, levels = c("metsch", "no metsch"),
                  labels = c("Parasites", "No parasites"))


chlorodata$metsch <- factor(chlorodata$metsch, c("No parasites", "Parasites"))

#Subset data
chlorodatametsch <- chlorodata %>%
  filter(metsch == "Parasites")

chlorodatanometsch <- chlorodata %>%
  filter(metsch == "No parasites")
```

```{r, plotting chlorophyll data}
chloroplotnometsch <- ggplot(chlorodatanometsch,aes(time,y=chloroln,group=chaoborus,color=chaoborus,shape=chaoborus)) +
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_cl_boot",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=2,aes(shape=chaoborus)) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred. dens.", shape = "Pred. dens.") +
  labs(y="LN chlorophyll \n(ug/L)") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw()+theme(panel.grid = element_blank()) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
      theme(legend.position = "none") +
     theme(axis.text.x=element_blank(),
          axis.title.x=element_blank()) +
     theme(axis.title.y=element_blank()) 

chloroplotnometsch

chloroplotmetsch <- ggplot(chlorodatametsch,aes(time,y=chloroln,group=chaoborus,color=chaoborus,shape=chaoborus)) +
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_cl_boot",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=2,aes(shape=chaoborus)) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred. dens.", shape = "Pred. dens.") +
  labs(y="LN chlorophyll \n(ug/L)") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw()+theme(panel.grid = element_blank()) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
      theme(legend.position = "none") +
     theme(axis.text.x=element_blank(),
          axis.title.x=element_blank()) +
     theme(axis.title.y=element_blank()) 

chloroplotmetsch

```

## Chlorophyll analysis
```{r, analysis of chlorophyll data}
#chlorophyll did very different things in first and second halves of the experiment

chlasummaryfirsthalf <- chlorodata %>%
  filter(time == 2 | time == 3 | time == 4 | time == 5) %>%
  group_by(chaoborus, metsch, tank) %>%
  summarise(meanchla = mean(chlorophyll),meanlnchla = mean(chloroln)) 
  
chlaov1 <- aov(meanchla~chaoborus*metsch,data=chlasummaryfirsthalf)
summary(chlaov1)  

overdisp_fun(chlaov1)
# super overdispersed

chlaov1b <- aov(meanlnchla~chaoborus*metsch,data=chlasummaryfirsthalf)
summary(chlaov1b)  

overdisp_fun(chlaov1b)
# not overdispersed

```

## Plot of average chlorophyll

```{r, average chlorophyll plot}
firsthalfchlsummaryplot <- ggplot(chlaov1b,aes(x=chaoborus,y=meanlnchla, color=chaoborus, fill = metsch)) +
  geom_boxplot(lwd=0.75) +
  geom_point(pch=17, position=position_jitterdodge(jitter.width = 0.2), alpha = 0.5, size = 2, color = 'black',show.legend=FALSE) +
    geom_text(data=chlaov1b,x=1.75, y=2.5,label ="Predation: p = 0.0005\nParasitism: p = 0.35\nPred*Para: p = 0.24", color="black",size = 2.5) +
  labs(x="Predator density (per L)",y="Average LN chlorophyll \nweeks 2-5 (ug/L)") +
  labs(color = "Predator density \n(per L)", fill = "Parasite treatment") +
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black"), guide="none") +
  scale_fill_manual(values=c('white','gray')) +
  theme_bw() +   
  theme(panel.grid=element_blank()) +
        theme(legend.position = "none") +
       theme(axis.text.x=element_blank(),
          axis.title.x=element_blank())

firsthalfchlsummaryplot


```

## Egg ratio plot

```{r, egg ratio data}
# Note added June 23 2022: discovered that the original eggdata.csv file was missing some data -- some data sheets didn't get entered (seems like they didn't get digitized and then data was entered from digitized data); recalculating averages from raw data; everything got thoroughly checked against raw data sheets in June 2022
raweggs<-readr::read_csv(here("data/raweggdata_6_22_22.csv"))
raweggsummary <- raweggs %>%
  group_by(tank, time) %>%
  summarise(meaneggs = mean(eggs), n=n()) 

# Kludge-y workaround -- exporting to add treatments, then will reimport with treatments added to data sheet
# readr::write_csv(raweggsummary, here("data/raweggsummary.csv"))

# now import summary data
eggs<-readr::read_csv(here("data/raweggsummary.csv"), na='.')


eggs$pred<-as.factor(eggs$pred)

# remove tank 22
eggs <- eggs %>%
  filter(tank != "22")

#Fix issue with weeks, so that they line up with this timeline:
#week 0 = Daphnia added
#week 1 = spores added
#weeks 2-9 = sampling
eggs$time <- eggs$time + 1

eggs$time<-as.factor(eggs$time)

summary(eggs)


#Subset data
eggsmetsch <- eggs %>%
  filter(para == "metsch")

eggsnometsch <- eggs %>%
  filter(para == "no metsch")
```

```{r, plotting egg data}

eggplotmetsch <- ggplot(eggsmetsch,aes(time,y=meaneggs,group=pred,color=pred,shape=pred)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_cl_boot",show.legend=FALSE) + 
  stat_summary(fun="mean",geom="point",size=2,aes(shape=pred)) + 
  scale_shape_manual(values=c(15,16,17,18)) + 
  labs(color="Pred.", shape = "Pred.") + 
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +  
  theme_bw()+theme(panel.grid = element_blank()) + 
  labs(y="Egg ratio \n(embryos per uninfected adult)") + 
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 5)) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) + 
      theme(legend.position = c(0.85, 0.64)) +
  theme(legend.key.size = unit(0.05, 'cm'), legend.title = element_text(size=7), #change legend title font size
        legend.text = element_text(size=6)) +
     theme(axis.text.x=element_blank(),
          axis.title.x=element_blank()) +
     theme(axis.title.y=element_blank()) 

eggplotmetsch

eggplotnometsch <- ggplot(eggsnometsch,aes(time,y=meaneggs,group=pred,color=pred,shape=pred)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_cl_boot",show.legend=FALSE) + 
  stat_summary(fun="mean",geom="point",size=2,aes(shape=pred)) + 
  scale_shape_manual(values=c(15,16,17,18)) + 
  labs(color="Pred.", shape = "Pred.") + 
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 5)) +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +  
  theme_bw()+theme(panel.grid = element_blank()) + 
  labs(x="Time (weeks)") + 
  labs(y="Egg ratio \n(embryos per uninfected adult)") + 
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) + 
      theme(legend.position = "none") +
     theme(axis.title.y=element_blank()) 

eggplotnometsch

```

## Egg ratio analysis

```{r, analysis of egg ratio data}
eggsummary <- eggs %>%
  drop_na() %>%
  group_by(pred, para, tank) %>%
  summarise(meaneggs = mean(meaneggs)) 
  
eggaov1 <- aov(meaneggs~pred*para,data=eggsummary)
summary(eggaov1)  

overdisp_fun(eggaov1)
# not overdispersed


eggsummary25 <- eggs %>%
  filter(time == 2 | time == 3 | time == 4 | time == 5) %>%  
  drop_na() %>%
  group_by(pred, para, tank) %>%
  summarise(meaneggs = mean(meaneggs)) 

eggaov25 <- aov(meaneggs~pred*para,data=eggsummary25)
summary(eggaov25)  

```

## Average egg ratio plot, weeks 2-5

```{r, egg plot for first half}
eggsummaryplot25 <- ggplot(eggaov25,aes(x=pred,y=meaneggs, color=pred, fill = para)) +
  geom_boxplot(lwd=0.75) +
  geom_point(pch=17, position=position_jitterdodge(jitter.width = 0.2), alpha = 0.5, size = 2, color = 'black',show.legend=FALSE) +
      geom_text(data=eggaov25,x=1.5, y=4.45,label ="Predation: p < 0.0001\nParasitism: p = 0.47\nPred*Para: p = 0.90", color="black",size = 2.5) +
  labs(x="Predator density (per L)", y="Average egg ratio weeks 2-5 \n(embryos per adult)") +
  labs(color = "Predator density \n(per L)", fill = "Parasite treat.") +
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black"), guide="none") +
  scale_fill_manual(values=c('white','gray')) +
  theme_bw() +   
  theme(panel.grid=element_blank()) +
        theme(legend.position = "none") 


eggsummaryplot25

```


## Combining into figure 3

```{r, making figure 3}
figure3panela <- (chloroplotmetsch / chloroplotnometsch) 
figure3panelc <- (eggplotmetsch / eggplotnometsch)


figure3 <- (figure3panela | firsthalfchlsummaryplot) /
  (figure3panelc | eggsummaryplot25) +
  plot_layout(ncol = 1) + 
  plot_annotation(tag_levels = list(c('a', ' ', 'b', 'c', '', 'd'))) 

figure3

ggsave(here("figures", "figure3.jpg"), figure3, units = "in", width = 7, height = 6, dpi = 300)


# Note: I added a few of the labels in photoshop because I couldn't get it to look nice in R

```

```{r, sample sizes for egg ratios}
eggratiosamplesizes <- eggs %>%
    group_by(pred, para, time) %>%
  summarise(meanhosts = mean(n)) 

eggratiosamplesizes2 <- eggratiosamplesizes %>% 
  group_by(pred, para, time) %>%
  summarise(meanhosts = mean(meanhosts)) 

eggratiosamplesizeshighpred <- eggratiosamplesizes %>% 
  filter(pred == 1) %>%
  group_by(para, time) %>%
  summarise(meanhosts = mean(meanhosts)) 

```

# Supplement figure: Evolutionary analyses

## Correlations between traits
```{r, correlations between pred and parasite susceptibility}
traitdata<-readr::read_csv(here("data/traits2.csv"))
str(traitdata)

traitsummary <- traitdata %>%
  summarise(meaninf = mean(inf.susc)) 

traitplot<-ggplot(traitdata, aes(x=inf.susc,y=pred.susc)) +
  geom_point(shape=16, size=3, color='black') +
  geom_smooth(method=lm,linetype='dashed', se=FALSE) +
  theme_bw()+theme(panel.grid = element_blank()) + 
  labs(x=expression(paste("Infection rate, "*beta*", ("*"*10"^"-7"*")"))) +
  labs(y=expression(paste("Pred. suscept., "*alpha*" ")))


traitplot

```

## Predation susceptibility
```{r, plotting susceptibility to predation over time}
predresevolplot<-ggplot(evoldata2,aes(round,y=predationmean,group=pred,color=pred,shape=pred)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) + 
  stat_summary(fun.data = "mean_cl_boot",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=4,aes(shape=pred)) +
  scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred. dens.", shape = "Pred. dens.") +
  scale_colour_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
  theme_bw()+theme(panel.grid = element_blank()) + 
  labs(x="Time (weeks)")+
  labs(y=expression(paste("Ave. pred. suscept., "*alpha*" "))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0))) +
  scale_x_continuous(breaks=c(0,2,6,9)) +
  facet_grid(rows=vars(para)) +
  theme(legend.position = "none") 
predresevolplot


# ggsave(here("figures", "predresevolplot.jpg"), predresevolplot, units = "in", width = 6, height = 3.5, dpi = 300)
```

## Predation susceptibility analysis

```{r, analyzing susceptibility to predation over time}
predmod1<-lme(predationmean~pred+para+round+pred*para+pred*round+para*round+pred*para*round,random=~1|tank,data=evoldata3)
summary(predmod1)
anova(predmod1)
lsmeans(predmod1,pairwise~round,adjust="tukey")
lsmeans(predmod1,pairwise~pred,adjust="tukey")
lsmeans(predmod1,pairwise~para,adjust="tukey")
```

## Plotting susceptibility to predation over time all on one panel
```{r, plotting susceptibility to predation over time all on one panel}
predresevolplottogether<-ggplot(evoldata2,aes(round,y=predationmean,group=para,color=para,shape=para)) + 
  stat_summary(fun="mean",geom="line",size=1,show.legend=FALSE) +
  stat_summary(fun.data = "mean_cl_boot",show.legend=FALSE) +
  stat_summary(fun="mean",geom="point",size=3,shape=21,aes(fill=para)) +
  labs(color="Parasitism", fill="Parasitism") +
  scale_colour_manual(values=c("black","black")) +
  scale_fill_manual(values=c("white", "#857A8C")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  labs(x="Time (weeks)") +
  labs(y=expression(paste("Ave. pred. suscept., "*alpha*" "))) +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) +
  scale_x_continuous(breaks=c(0,2,6,9)) +
  theme(axis.title.x=element_text(margin=margin(t=10,r=0,b=0,l=0)))  +
    theme(legend.position = c(0.3, 0.8)) +
  theme(legend.key.size = unit(0.05, 'cm'), legend.title = element_blank(),
        legend.text = element_text(size=8)) 
predresevolplottogether
```

## Combining to make supplement figure S1
```{r, making supplement figure S1}
evolutionplot <- traitplot + predresevolplot + predresevolplottogether +
  plot_layout(ncol = 1) + 
  plot_annotation(tag_levels = 'a') 
evolutionplot

ggsave(here("figures", "evolutionplot.jpg"), evolutionplot, units = "in", width = 3, height = 7, dpi = 300)
```


# Stage structure -- this is Figure S2
```{r, looking at stage structure}
stagetimeplot <- ggplot(indianadata, aes(x = time, y = (propadults), color = chaoborusfactor, group = chaoborusfactor, shape = chaoborusfactor)) + 
  stat_summary(fun = "mean", geom="line", aes(group = chaoborusfactor)) + 
  stat_summary(fun.data="mean_se") +
    stat_summary(fun="mean",geom="point",size=4,aes(shape=chaoborusfactor),show.legend=FALSE) +
  facet_grid(rows=vars(metsch)) +
  labs(x="Time (week)",y="Proportion adults") + 
  scale_x_discrete(limits=c("1", "2","3","4","5","6","7","8","9")) + 
  scale_color_manual(values=c("#6baed6", "#3182bd", "#08519c","black")) +
    scale_shape_manual(values=c(15,16,17,18)) +
  labs(color="Pred.", shape = "Pred.") +
  theme_bw()+theme(panel.grid = element_blank()) +
    theme(legend.position = c(0.07, 0.63)) +
  theme(legend.key.size = unit(0.05, 'cm'), legend.title = element_text(size=10), 
        legend.text = element_text(size=8)) 

stagetimeplot

ggsave(here("figures", "SuppAgeStructure.jpg"), stagetimeplot, units = "in", width = 5, height = 4, dpi = 300)
```




